---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bldRpckgw2

[![Build Status](https://travis-ci.com/ElliottMess/bldRpckgw2.svg?token=RphAcb7xKsmCuGe5zzCq&branch=master)](https://travis-ci.com/ElliottMess/bldRpckgw2)

This package aims at facilitating the use of the [US National Highway Traffic Safety Administration's Fatality Analysis Reporting System](http://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)}{US National Highway Traffic Safety Administration's Fatality Analysis Reporting System).

## Installation

You can install the released version of bldRpckgw2 from [GitHub](https://github.com/ElliottMess/bldRpckgw2) with:

``` r
# install.packages("devtools")
devtools::install_github("ElliottMess/bldRpckgw2")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(bldRpckgw2)

 fars_summarize_2014 <- fars_summarize_years(2014)
 fars_map_NY_2014 <- fars_map_state(50, 2014)
```
